A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-16 documents/plm.tex
tilde

\title{%
  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
}
\author{%
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
  Tom~Barclay\altaffilmark{\ref{Ames}},
  Rob~Fergus\altaffilmark{\ref{Courant}},
  Stefan Harmeling\altaffilmark{\ref{MPIIS}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
  others%
}

>>>>

\title{%
  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
}
\author{%
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
  Tom~Barclay\altaffilmark{\ref{Ames}},
  Rob~Fergus\altaffilmark{\ref{Courant}},
  Stefan~Harmeling\altaffilmark{\ref{MPIIS}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
  others%
}
